SAT Competition 2020\tnoteref{title}

### 2020-12-17 paper/main.tex

@@

\multirow{4}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}} & \multirow{3}{*}{Kissat-sc2020} &  -- & \firsto\firstu\\
 &  &  sat & \firsto\firstu\seconds\\
 &  &  unsat & \firstu\thirdp\\
\cline{2-4}
 &  CaDiCaL-sc2020 &  -- & \\
\hline

>>>>

\subsection{Observations}

@@

\multirow{4}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}} & \multirow{3}{*}{Kissat} &  -- & \firsto\firstu\\
 &  &  sat & \firsto\firstu\seconds\\
 &  &  unsat & \firstu\thirdp\\
\cline{2-4}
 &  Cadical & SC2020 & \\
\hline
